\begin{thebibliography}{99}
%chapter1
\bibitem{bib:chess}
    J. McCarthy. (2007) 
    ``What is Artificial Intelligence?'', 
    \url{http://www-formal.stanford.edu/jmc/whatisai/whatisai.html} (Accessed 2023/10/31).
\bibitem{bib:AplpaGo}
    D. Silver, A. Huang, C. J. Maddison et al. (2016) 
    Mastering the game of Go with deep neural networks and tree search, 
    Nature volume 529, pp.484-489.
\bibitem{bibAlphaStar}
    O. Vinyals, I. Babuschkin, W. M. Czarnecki et al. (2018) 
    Grandmaster level in StarCraft II using multi-agent reinforcement learning, 
    Nature volume 575, pp.350-354, 2019.
\bibitem{bib:maia}
    R. McIlroy-Young, S. Sen, J. Kleinberg, A. Anderson. (2020) 
    Aligning Superhuman AI with Human Behavior: Chess as a Model System,
    KDD '20: Proceedings of the 26th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, pp 1677-1687.
\bibitem{bib:craft_assist}
    J. Gray, K. Srinet, Y. Jernite et al. (2019) 
    Craftassist: A framework for dialogue-enabled interactive agents,
    arXiv preprint arXiv:1907.08584.
\bibitem{bib:Minecraft}
    Mojang Studios. (2023)
    ``Minecraft'', 
    \url{https://www.minecraft.net/ja-jp} (Accessed 2023/11/12).
\bibitem{bib:minecraft_news}
    Yahooニュース. (2023)
    ``『マインクラフト（Minecraft）』の累計売り上げが3億本を突破！史上最も売れたインディーゲーム，不動の地位を築く'',
    \url{https://news.yahoo.co.jp/articles/81edc817187b79350186eed8b5219f6be51a3ac7} (Accessed 2023/11/12).
%chapter2
\bibitem{bib:minecraft_creative tool}
	M. Cipollone, C. C. Schifter, R. A. Moffat. (2014) 
    Minecraft as a Creative Tool: A Case Study, 
    International Journal of Game-Based Learning 4(2), pp.1-14.
\bibitem{bib:arlpcg}
	L. Gisslén, A. Eakins, C. Gordillo et al. (2021)
    Adversarial Reinforcement Learning for Procedural Content Generation,
    2021 IEEE Conference on Games (CoG), pp1-8.
\bibitem{bib:gancraft}
	Z. Hao, A. Mallya, S. Belongie, M. Y. Liu. (2021) 
    GANcraft: Unsupervised 3D Neural Rendering of Minecraft Worlds, 
    Proceedings of the IEEE/CVF International Conference on Computer Vision, pp.14072-14082.
\bibitem{bib:voyager}
    G. Wang, Y. Xie, Y. Jiang et al. (2023)
    Voyager: An Open-Ended Embodied Agent with Large Language Models, 
    arXiv preprint arXiv: Arxiv-2305.16291.
%chapter3
\bibitem{bib:curseforge}
    Overwolf. (2024) 
    ``CurseForge - Minecraft Mods \& Modpacks'',
    \url{https://www.curseforge.com/minecraft} (Accessed 2024/01/09).
\bibitem{bib:eula}
    Mojang Studios. (2023)
    ``Minecraft End(er)-User License Agreement (``EULA'')'',
    \url{https://www.minecraft.net/en-us/eula} (Accessed 2024/01/09).
\bibitem{bib:minecraft_edu}
    Mojang Studios, 
    ``Minecraft Education'', 
    \url{https://education.minecraft.net/ja-jp} (Accessed 2024/01/08).
\bibitem{bib:fun_minecraft_server}
    S. Kabashima, K. Matsuda, R. Yamamoto, I. Frank. (2023) 
    Building a Better World: Lessons from Setting up, Maintaining and Developing a University Minecraft Server, 
    JSET Autumn Conference 2023 collection papers. pp.597-598.
\bibitem{bib:fun_minecraft_server_research}
    K. Kudo, K. Matsuda, I. Frank, D. K. Bagenda. (2023)
    Research and Education Through a Minecraft Testbed: Character, Bots and ChatGPT,
    JSET Autumn Conference 2023 collection papers. pp.595-596.
%chapter4
\bibitem{bib:Mineflayer}
    PrismarineJS. (2024) 
    ``Github - PrismarineJS/mineflayer'', 
    \url{https://github.com/PrismarineJS/mineflayer} (Accessed 2024/01/09).
\bibitem{bib:few-shot}
    T. Brown, B. Mann, N. Ryder et al. (2020) 
    Language Models are Few-Shot Learners, 
    Advances in neural information processing systems volume 33, pp.1877-1901.
\bibitem{bib:rag}
    P. Lewis, E. Perez, A. Piktus et al. (2020) 
    Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks, 
    NeurIPS.
\bibitem{bib:function_calling}
    OpenAI. (2024)
    ``Function calling -Documentation'',
    \url{https://platform.openai.com/docs/guides/function-calling} (Accessed 2024/01/09).
\bibitem{bib:prismarine-nbt}
    PrismarineJS. (2023) 
    ``Github - PrismarineJS/prismarine-nbt: An NBT parser for node-minecraft-protocol'', 
    \url{https://github.com/PrismarineJS/prismarine-nbt} (Accessed 2024/01/09).
\bibitem{bib:fine-tuning}
    OpenAI. (2024) 
    ``OpenAI API - Fine-tuning'', 
    \url{https://platform.openai.com/docs/guides/fine-tuning} (Accessed 2024/01/09).
%chapter5

%chapter6

%chapter7





\end{thebibliography}
