% TODO: 英文アブストラクトを以下の{}内に記述（以下はダミーテキスト）
\newcommand{\eabstract}{

Games have long been important as a testbed and basic research for improving the performance of artificial intelligence and algorithms, and in recent years AI has surpassed human scores in complex games such as Go. 
However, even though AI has overwhelmed humans, game research is still valuable as a testbed and basic research, and new approaches, such as human-AI cooperation, are being seen. 
This research aims to explore the boundaries and possibilities of cooperation and collaboration between humans and AI in the context of ever-changing artificial intelligence technologies, and has developed a bot "Mason" (Minecraft AI Support - Objectives and Novelty) that works with players in the virtual 3D game "Minecraft" using the ChatGPT API. 
which can suggest the next task suitable for the current situation by observing the player's information and conversations with the player. 
It can also generate and customise structures such as houses and furniture in the gameplay world by issuing Minecraft fill commands according to user instructions. 
When these functions were tested, the LLM's spatial grasp and response performance suggested the boundaries of the current cooperation and collaboration between humans and AI. 
The ability to embed bot functions in virtual space is rapidly expanding, and these results can be seen as an early stage in the activity of embedding bots in virtual space. 
Minecraft also has applications as an educational tool, and Mason's potential for human-AI cooperation is that Mason can introduce students to the basics of virtual worlds Mason could be useful for introducing students to the basics of virtual worlds, developing their creativity and communication skills, and familiarising them with LLMs. 
Future plans include the need to improve the prompts to allow for more complex structures to be generated and interacted with, and for stronger inspiration and competence; the Mason framework is publicly available and could be adapted by others to explore the creative The possibility of exploring the perspectives enabled by the development of generative AI is also conceivable.

}